\documentclass[10pt]{letter}
\usepackage{palatcm}

\address{Samuel Halliday\\
  4F2 15 Warrender Park Terrace\\
  Edinburgh EH9 1EG}
\signature{Samuel Halliday}

\begin{document}
\begin{letter}{Dean Professor Brian Austin\\
School of Life Sciences\\
Heriot-Watt University\\
Edinburgh EH14 4AS}
\opening{Dear Professor Austin,}

I have recently completed a Ph.D. in Mathematics at Heriot-Watt University and
despite several years of very enjoyable research, I am leaving with a bitter
taste in my mouth. This is due to my final moments; the thesis submission and
graduation process.

The submission of my thesis was without a doubt the most infuriating experience
of my life. I have attempted to capture my nightmare so that you may be made
aware of the reality of submitting a thesis at Heriot-Watt. Please consider my
comments as constructive feedback.

Submitting a Ph.D. thesis marks the end of several years of research and should
therefore be an enjoyable and relieving experience. Many other universities
celebrate this by having helpful submissions staff go to great lengths in order
to make the process as simple as possible, even providing ``well done, but
what's next?'' literature upon initial and final submission. But not at
Heriot-Watt.

My initial submission was a nightmare costing me three full days away from my
new employment. The reason for this was because the staff refused to accept my
thesis before they had received the ``appointment of external examiner'' form,
\textit{which they had lost}! I do not understand why the staff could not simply
hold my thesis until they had obtained the replacement letter instead of
requiring me to take another day off work. I politely brought this to their
attention at the time and gained no sympathy from them.

Heriot-Watt is quite inconveniently located, the submissions desk staff should
be more accommodating because of this. I made it quite clear that I would have
to take time off from work in order to travel out so far.

Upon submission I innocently asked what I should expect next, to which I was
told ``you will get corrections from your examiner''. \textbf{This information
  was completely inaccurate}. The process is such that an examination will be
arranged with an external and an internal examiner. The staff clearly need to be
educated on correct procedure. What I actually wanted to know was if I would be
updated when the thesis had arrived with the correct people. Given how anxious
the student may be, I would suggest implementing a feedback system so that they
may hear when the thesis is received by the examiners. To avoid this potential
pitfall, I simply resorted to e-mailing a digital version of my thesis to my
examiners.

I thought it best to bring my final version for a check-up before it was hard
bound. It was very lucky that I did, because I was informed that I would have
been asked to resubmit my (\pounds 90) set of theses and miss the submission
deadline because the Acknowledgements page was at the back of my thesis, instead
of the front! \textit{To reject a thesis on these grounds is appalling and
  Heriot-Watt should be ashamed of themselves for being so pedantic}. It is
standard practise in mathematics to place acknowledgements at the end of a
publication. The rules and regulations are set up in order to meet library
requirements for filing and to ensure that the correct people have signed off on
a final document in order to avoid falsification. The rules \textbf{do not}
exist so that the submissions staff can have a final say on whether a student
graduates.

My final submission required me to take two more days off from work; first to
have the check made and the second to actually submit (not counting a third to
collect the bound thesis). But upon submission, the staff were not initially
willing to process my thesis because I had not brought the correct British
Library submission form. As this is a simple and trivial form to complete I
simply suggested they print me a copy and I could fill it out there and then.
They plain refused, despite me humiliatingly begging them as I had a meeting to
attend and was on a tight schedule. By this stage I had returned my office keys
and had to spend a considerable amount of time hunting down a computer and
printer which I still had access to. I was completely shocked that anyone could
be so unhelpful! May I suggest that the staff be instructed to help students as
much as possible to the extend of printing off these peripheral forms; it is not
much to ask. The staff's attitude was one of obstruction and I would go so far
as to say they were just plain rude.

These issues combined with the hidden graduation costs of \pounds 190 = \pounds
20 (temporary binding) + \pounds 90 (final binding) + \pounds 45 (graduation) +
\pounds 35 (gown hire), makes for a very unpleasant experience altogether. I
would also like to point out that the letter confirming graduation ``subject to
the senate'' arrived only two days prior to my graduation day! This means that
the above expenses, plus family travel and board, where all for a speculative
graduation! This lack of proper notice is absurd.

I am very displeased with the service Heriot-Watt's thesis submissions staff
provide and I would strongly suggest that the following main points be addressed
so that future generations of students do not have the same bitter experience as
I have:-
\begin{itemize}
\item Implement a feedback system. An e-mail to alert students that their thesis
  has been sent to (preferably received by) their examiner would be sufficient.
  Further feedback, details and sufficient notice for the graduation process and
  ceremony should also be provided.
\item Train the staff on how to deal with the public and educate them on the
  mental and financial state of the students they are dealing with.
\item Demote the frivolous points of the thesis submissions rules to
  ``recommendations'' in order to avoid ridiculous rejections.
\item Make the process of submission an enjoyable final moment at Heriot-Watt,
  not one that taints several years of enjoyable research.
\end{itemize}

Failing to allow doctorate students to complete the submission process in a
convenient and enjoyable manner will only lead to a smearing of Heriot-Watt's
reputation and is therefore a serious issue.

\closing{Yours sincerely,}

\end{letter}
\end{document}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
