{\Large Acknowledgements}

Above all, I would like to thank my supervisor Professor R. J. Szabo for this
project and for his continued support even when the elusive time dependent
noncommutative geometry seemed impossible to find. I'd also like to express my
appreciation to E.P.S.R.C., the body responsible for my funding.

Many thanks to all the friends I've made during this time in Edinburgh who have
been there through the good times and the bad times (in no particular order, and
by no means exhaustive); Mick, Eddie \& Cheryl, Murdoch, Andy, Lainy, Alana,
Sharon, Damien, Ross, Brian, Scott, Fullie, Gav, Tom, Henry, Helen, Erik,
Carolyn, Cian, Jimbo, Jessica, Emma, Georgios, Isabelle, Becca and Shug Boabby.

Further thanks go to those who have been around for a lot longer and came to
visit; Laffy \& Aine, Timbo, Qagi, Mark \& Sarah (in fact, the whole F.H.S.S.T.
crew), Rors, Ben, Jules, Claire, Heath, Beggsy, Steve, Nick and Keith. Special
thanks go to my fantastic girlfriend, Lesley.

I'd also like to thank Dr. D. Clark for inspiring me to pursue a dream and to
Hannu, Dan and Angela for being crazy enough to think that it might just work.
Thanks to Professor J. Simmons and Professor A. Lacey for their help in getting
``ThinkTank Mathematics Limited'' off the ground.

Finally, thanks to my parents for giving me the chances in life to make it this
far and to the big man upstairs who is always looking out for me.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "main.tex"
%%% End: 
