%\documentclass[11pt, a4paper]{article}
%\begin{document}
\thispagestyle{empty}
\begin{center}
 \Large{\bf Changelog from Initial Submission to Final\footnote{To aid examiners only, please discard this section before final submission.}}
\end{center}
\texttt{
\tiny
\begin{enumerate}
\item[-] Removed section 7, updated rest of text accordingly.
\item[-] Rearranged section 6.4.3 and upgraded to a full section entitled `A Toy Model' to show that this standard model treatment
	 has major problems before starting. Also change the goals in section 1.5 to reflect my stance with this model.
\item[-] Section 6.5.1 reworded in order to point to the need of a central object and the problem this poses to the fermion ball scenario.
\item[-] Section 9 removed text on new technique.
\item[-] Section 1.1 removed incorrect `discrepancy with theory' sentence.
\item[-] Section 1.2 removed sentence entirely.
\item[-] Figure 5 changed IR to FIR, removed data point. Also in Figures 29-31.
\item[-] Section 1.2 added extra reference to Fermion ball studies.
\item[-] Added reference in Figure 7 at request.
\item[-] Unable to add units to Figure 12 as this is directly from astro-ph/0106209.
\item[-] Section 5.2 changes, but refuse to amend typo to `afterward' (sic)
	 as that is an Americanism. `Afterwards' is the preferred correction :D.
\item[-] Corrections to 5.3 not added as 5.4 points out clearly that the fermion ball scenario does not
	 provide an obvious minimum to the $\chi^2$. This can also be seen from figures 15, 17 and 19 being
	 almost entirely blue, meaning a good fit for either of the 2 parameters. Tables 1-3 cannot
	 possibly contain all the information of these plots. Added a sentence of this effect to 5.3.2.
	 Changed wording of 5.4.
\item[-] Section 6.1 Km/s to km/s
\item[-] Section 6.5 amended standard theory conclusions.
\item[-] References made more self-consistent.
\item[-] Section 5.1 added word `general' to not discount the incredibly rare possibility of closed 1D `harmonic oscillator'
	 solutions and emphasised the precession as the main distinguishing feature.
\item[-] Section 5.2 added clarity to comment about movement of Sgr A*.
\item[-] Section 6.1 added `cluster of stars' at request.
\item[-] Changed abstract to mention that Sgr A* does not meet the requirements for the standard model.
	 Emphasised the word simple and added a note about ADAF models.
\item[-] Section 1.2 grammar.
\item[-] Figure 2 added label and zoomed in.
\item[-] Figure 4 added extra information.
\item[-] Section 1.3 grammar.
\item[-] Equation 2 fixed typo.
\item[-] Section 5.3.1 reworded.
\item[-] Section 6.1 reworded.
\item[-] Section 6.2 fixed typo.
\item[-] Section 6.3 fixed typo.
\item[-] Section 6.5.2 more problems highlighted.
\item[-] Appendix B fixed.
\item[-] Moved Feynman diagram to section 7.
\item[-] Added a preface entitled "A Pinch of Salt".
\end{enumerate}
}
\clearpage
%\end{document}
